As the semester comes to an end, one last thing to do for this class is to report passed students to the current course coordinator of ECE210. Keep in mind that course coordinator and course director are usually two different concepts. Typically there is only one course director for one course, and this Professor will always be the course director for this course even he is not teaching this course anymore. However, there can be many different course coordinators, even there is only one for each semester. For each semester, one professor or faculty currently teaching this course will become the course coordinator.

To report the passed students to the course coordinator, my suggestion is to assemble a list of students who have passed with all the necessary information included: name, NetID, and lecture section. These information will help the course coordinator award honors credit to passed students. To assemble such a list, the fastest and easiest way is to use Excel, but you can also use HTML table, Origin, Word, or other software you wish.

I would recommend you to report grades near reading day. This is because you want to allow a few more days for students to finish and demonstrate the final assignment, but at the same time you want to provide this information to the course coordinator early. Professors are usually very busy and have very packed schedule, so you want to make sure that they have all the information they need when they get to manage the honors credit. Bottom line, report the grades to the course coordinator as soon as the class is finished and all the students are done with the final assignment.
